### 2008-12-20 talk/ecoop2009/intro.tex
expand a bit the idea of jit layering in the introduction

The contributions of this paper are \emph{promotion}, a generalization of
polymorphic inline caches that make partial evaluation practical for dynamic
languages and trying out the idea of JIT-layering XXX.

>>>>

Instead of emitting code for a real CPU, the generated JIT compilers described
in this paper emit code for a virtual machine: before being executed, the
emitted code will be compiled again by .NET's own JIT compiler, thus having
two \emph{layers} of JIT compilation.

The contributions of this paper are twofold: (1) \emph{promotion} is a
generalization of polymorphic inline caches that make partial evaluation
practical for dynamic languages; (2) we demonstrated that the idea of
\emph{JIT layering} can give good results, as dynamic languages can be even
faster than their static counterparts.
